### 2016-09-17 thesis/methods/methods.tex
tmp commit

The samples were grouped based on the sample BMI status (obese or non-obese group), and a linear model was fitted to the data based on the sample grouping.
Empirical Bayes statisticsc was used to identify the differentially expressed genes between the two groups, and the top scoring genes were listed.
The error rate of the genes were \gls{fdr} controlled for multiple hypothesis testing.

@@

>>>>

The samples were grouped based on the sample BMI status (obese or non-obese group), and a linear model was fitted to the data based on the sample grouping.
Empirical Bayes statistics was used to identify the differentially expressed genes between the two groups, and the top scoring genes were listed.
The error rate of the genes were \gls{fdr} controlled for multiple hypothesis testing.

@@

All 18 pathway signatures from \citet{Gatza2010a} study were used to create both the metagenes and transformation matrices in the Gatza data set.
Each of the 18 pathway metagenes were compared with the gene expression of the gene that represents the pathway to check whether the metagenes were in the correct direction.
% TODO: check if it was the AKT1 or AKT2 gene for AKT pathway
For example, the AKT pathway metagene was compared with the AKT1 gene expression.

The metagenes were flipped depending on the
